---
title: "A reproducible measurement report"
format:
  html:
    embed-resources: true
execute:
  echo: true
---

## Question and inputs

What is the mean of the four synthetic measurements in measurements.csv?
These values illustrate the workflow; they are not research observations.

```{r}
measurements <- read.csv("measurements.csv")
stopifnot(identical(names(measurements), "value"))
stopifnot(is.numeric(measurements$value))
stopifnot(nrow(measurements) == 4L, !anyNA(measurements$value))
stopifnot(all(is.finite(measurements$value)))
result <- mean(measurements$value)
stopifnot(result == 5)
cat(sprintf("count=%d\nmean=%.1f\n", nrow(measurements), result))
```

## Inspect the measurements

```{r}
plot(seq_len(nrow(measurements)), measurements$value,
     type = "b", xlab = "Measurement number", ylab = "Value")
abline(h = result, col = "blue", lty = 2)
```

## Result and interpretation

The four supplied values have mean 5.0. This example checks a calculation;
it does not estimate uncertainty or establish a scientific conclusion.

## Environment used to render this report

```{r}
sessionInfo()
```
